Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-04 paper.tex
Add section 3 on delegation schemes
Add reference by Gheorghiu and Vidick
Add tentative definitions
Definitions of characteristics quantum delegation schemes might have

@@

>>>>

\section{Quantum Delegation Schemes}

Here we describe schemes that allows a classical client to interact with a quantum server, and various properties that such schemes can have.

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a possibly malicious BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input. Its goal is to evaluate the quantum circuit with an honest prover.
\end{definition}

\begin{definition}
	A quantum delegation protocol has \emph{long output with error $\epsilon$} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register. Said result's probability distribution would be within $\epsilon$ of the true distribution.
\end{definition}

\begin{definition}
	A quantum delegation protocol is \emph{blind} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
\end{definition}

\begin{definition}
	A quantum delegation protocol is \emph{verifiable} if the verifier can check if the output is correct. TODO need to be more rigorous here.
\end{definition}

@@

	\bibitem{1904.06320}
	Alexandru Gheorghiu and Thomas Vidick.
	\newblock Computationally-secure and composable remote state preparation, 2019;
	\newblock arXiv:1904.06320.
